From Object Classification to Naming: Modeling Entry-level Names for Real-world Objects

### 2019-12-09 papers/ACL2020/introduction.tex

Objects, being members of many categories, can be called by many names (e.g.,\ a duck can be called \name{duck, bird, animal} etc.). 
The task of \emph{object naming} -- generating not just a formally correct but also an appropriate, \emph{natural} name for an object -- is distinct from the closely related tasks of object detection and image classification (see below).
It has been studied in psycholinguistics~\cite{refs} \mw{Refs!}, but has received comparatively little attention in \langvis (\lv) and computational linguistics (CL) research.
We address the following question:\\
\fbox{\parbox{\columnwidth}{\textbf{Q:} Can standard object detection/image classification models (be fine-tuned to) exhibit human-like object naming behavior?}}\\\\
In particular, we test several models for their ability to generate \emph{entry-level names}, i.e., the names people prefer when calling a specific object (e.g.,~\name{duck} in Figure~\ref{fig:duck}, right image).
We wish to find out, for instance, whether different types of models or training regimes will tend towards different kinds of human-like errors in this regard.
A secondary contribution of this paper is instrumental: for a proper evaluation we must first augment an existing human object naming dataset (\mn, Anonymous, under review) with extensive quality control, the resulting data of which we also describe and make available with this paper.

@@

% By contrast, the goal of \lv object naming models is to predict the `natural' name of an object, i.e.,~the name a human could choose for the object instance.
Psycholinguistic studies have found that humans have a preference towards a particular name, defined as the \textit{entry-level name}, when naturally naming an object \cite{rosch1976basic,Rosch1978,jolicoeur1984pictures}. 
However, this research has traditionally focused on \categories and/or their prototypical/schematic depictions (e.g., \newcite{rossion2004revisiting}), as opposed to the situated instances in naturalistic images with which \lv is mostly concerned.
Humans may prefer different names for different instances of the same \category, and have them even disagree in their choice for the same instance (see also \citealt{graf2016animal}).
For example, in Figure~\ref{fig:duck}, for the two instances of a duck (from \vg, with names from \mn), most people (27 out of 36) called the instance on the left \name{bird}, while \name{duck} was strongly preferred for the right instance. 
\begin{figure}[t]
	\centering
	\small
	\begin{tabular}{p{3cm}p{3cm}}
		\centering
		\includegraphics[scale=0.15]{images/2327551_2960743_seed_ambiguous.png} &
		\includegraphics[scale=0.15]{images/2358126_805887_singleton_obj.png}\\
		bird\ (27),  duck\ (8) & duck (33), bird (3)\\
	\end{tabular}
	\caption{Different naming preferences for different instances of the same \category \name{duck} in \mn.\label{fig:duck}}
\end{figure}
Hence, both the single-ground-truth view of CV models and the category-level approach predominant in Psycholinguistics are insufficient for assessing the effectiveness of \lv models for human-like, entry-level object naming.
The \mn dataset was designed to help mend this gap: it consists of names entered by 36 annotators in parallel, for 25K objects in naturalistic images from \vg~\cite{krishna2016visualgenome}.
However, the name annotations of \mn have not been verified to filter out incorrect names or names for the wrong object, a problem that is in some sense the opposite of that posed by the single-ground-truth approach.

Our main contributions in this paper are (i) to run the \mn data through a rigorous annotation round to quantify both the adequacy of its names and the types of errors they contain, in order to (ii) test and compare object detection and image classification models for their ability at the task of \emph{instance-based, entry-level object naming}. More precisely, \mn enables us to define the entry-level as follows:\\
\fbox{\parbox{\columnwidth}{\textbf{Entry-level name:} the most common name given to an object instance according to \mn}}\\\\
We evaluate the effectiveness of different models on predicting these entry-level names, and our additional verification annotations enable us to understnad the kinds of mistakes each model makes (e.g.,~a `wrong' prediction may be a less preferred name as opposed to a true error).
We show that generic object classification models on their own (ResNet, Faster-RCNN and Bottom-up) already learn to provide entry-level names for objects, but also that it is possible to apply transfer learning on \mn, successfully using pre-trained features from object detection and image classification models to train entry-level naming models. 
\mw{Remark about the kinds of human errors, just as in the abstract, or some other more interesting teaser?}

>>>>

Objects, being members of many categories, can be called by many names (e.g.,\ a duck can be called \name{duck, bird, animal} etc.). 
The task of \emph{object naming} -- generating not just a formally correct but also an appropriate, \emph{natural} name for an object -- is distinct from the closely related tasks of object detection and image classification (see below).
It has been studied in psycholinguistics~\cite{refs} \mw{Refs!}, but has received comparatively little attention in \langvis (\lv) and computational linguistics (CL) research.
We address the following question:\\
\fbox{\parbox{\columnwidth}{\textbf{Q:} Can standard object detection/image classification models (be fine-tuned to) exhibit human-like object naming behavior?}}\\\\
In particular, we test several models for their ability to generate \emph{entry-level names}, i.e., the names people prefer when calling a specific object (e.g.,~\name{duck} in Figure~\ref{fig:duck}, right image).
%% SHORTENING %% We wish to find out, for instance, whether different types of models or training regimes will tend towards different kinds of human-like errors in this regard.
A secondary contribution of this paper is instrumental: for a proper evaluation we must first augment an existing human object naming dataset (\mn, Anonymous, under review) with extensive quality control, the resulting data of which we also describe and make available with this paper.

@@

% By contrast, the goal of \lv object naming models is to predict the `natural' name of an object, i.e.,~the name a human could choose for the object instance.
Psycholinguistic studies have found that humans have a preference towards a particular name, defined as the \textit{entry-level name}, when naturally naming an object \cite{rosch1976basic,Rosch1978,jolicoeur1984pictures}. 
However, this research has traditionally focused on \categories and/or their prototypical/schematic depictions (e.g., \newcite{rossion2004revisiting}), as opposed to the situated instances in naturalistic images with which \lv is mostly concerned.
Yet humans may prefer different names for different instances of the same \category, and have them even disagree in their choice for the same instance (see also \citealt{graf2016animal}).
For example, in Figure~\ref{fig:duck} most people (27 out of 36) called the duck on the left \name{bird}, while \name{duck} was strongly preferred for the duck on the right. 
\begin{figure}[t]
	\centering
	\small
	\begin{tabular}{p{3cm}p{3cm}}
		\centering
		\includegraphics[scale=0.15]{images/2327551_2960743_seed_ambiguous.png} &
		\includegraphics[scale=0.15]{images/2358126_805887_singleton_obj.png}\\
		bird\ (27),  duck\ (8) & duck (33), bird (3)\\
	\end{tabular}
	\caption{Different naming preferences for different instances of the same \category \name{duck} in \mn.\label{fig:duck}}
\end{figure}
Hence, both the single-ground-truth view of CV models and the category-level approach predominant in Psycholinguistics are insufficient for assessing the effectiveness of \lv models for human-like, entry-level object naming.
The \mn dataset was designed to help mend this gap: it consists of names entered by 36 annotators in parallel, for 25K objects in naturalistic images from \vg~\cite{krishna2016visualgenome}.
However, the name annotations of \mn have not been verified to filter out incorrect names or names for the wrong object, a problem that is in some sense the opposite of that posed by the single-ground-truth approach.

Our main contributions in this paper are (i) to run the \mn data through a rigorous annotation round to quantify both the adequacy of its names and the types of errors they contain, in order to (ii) test and compare object detection and image classification models for their ability at the task of \emph{instance-based, entry-level object naming}. More precisely, \mn enables us to define the entry-level as follows:\\
\fbox{\parbox{\columnwidth}{\textbf{Entry-level name:} the most common name given to an object instance according to \mn}}\\\\
We evaluate the effectiveness of different models on predicting these entry-level names, and our additional verification annotations enable us to understnad the kinds of mistakes each model makes (e.g.,~a `wrong' prediction may be a less preferred name as opposed to a true error).
We show that generic object classification models on their own (ResNet, Faster-RCNN and Bottom-up) already learn to provide entry-level names for objects, but also that it is possible to apply transfer learning on \mn, successfully using pre-trained features from object detection and image classification models to train entry-level naming models. 
%% SHORTENING %% \mw{Remark about the kinds of human errors, just as in the abstract, or some other more interesting teaser?}

### 2019-12-09 papers/ACL2020/related.tex

%\paragraph{(Entry-Level) Object Naming}
%cognitive science/psychology:\\
%- levels of specificity\\
%- basic-level vs. entry-level\\ 
%- object naming studies
%
%Language + Vision:\\
%Ordonez et al., Zarriess \& Schlangen, ... \\
%- Our work: empirical notion of entry-level
%\cs{Necessary to say something about class vs. category? Otherwise I would just always use class to make things easier.}
Our work on natural object naming connects research in psycholinguistics, \langvis and computer vision. In psycholinguistics, studies of picture naming have found that humans identify objects at a preferred level of abstraction, the so-called basic-level \cite{rosch1976basic,jolicoeur1984pictures}. 
The typicality of the object with respect to this basic-level \category is important for determining the preferred name, i.e.\ the entry-level name: highly typical objects (e.g.,\ a robin) are simply named by their basic-level \category (\name{bird}), while atypical objects (e.g.,\ \name{penguin}) are preferably named by the more specific category.
%% This strictly taxonomic view suggests that entry-level names generally hold for all instances of a \category (e.g.,\ penguin).   \mw{Not true!!}
\newcite{Ordonez:2016} take up this view and train a model to map an object's \category detected by an object recognition system to its natural name, guided by external resources like corpus statistics.
By contrast, we rely on the \mn dataset (more details below) to directly test as well as fine-tune object recognition (and image classification) systems, and without presupposing a taxonomical relationship between the possible names for an object.

@@

\cs{Need to check Jolicoeur and their experiments; say sth about shared visual features}
% prototypical visual features common to all its instances (e.g.,\ apples are round, pears are ... (CHECK)).

In Computer Vision a major focus is visual object recognition, with object classification being a core task in this area. 
Neural object classification systems are trained to label the most salient object in an image and often use the ImageNet \cite{imagenet_cvpr09} benchmark that labels images/objects with 1000 fine-grained classes \cite{googlenet,he2016deep}). 
These neural object classifiers have proven extremely useful in a large range of transfer learning scenarios. 
They are commonly used as pretrained feature extractors in object detection systems that localize objects and predict their labels \cite{fasterrcnn2015}.
For instance, a commonly used object detector in \lv is \citep{anderson2018updown}'s so-called bottom-up model, which is based on a pretrained ResNet classification and finetunes Faster-RCNN \cite{fasterrcnn2015} for object detection and classification on \vg. 
We will use pretrained ResNet, Faster-RCNN and Bottom-up as models in this paper, extending and testing them for entry-level object naming.

\paragraph{The ManyNames dataset}
As mentioned we will rely heavily on the \mn dataset (Anonymous, under review), which builds upon object annotations in \vg.
\mn provides up to 36 name annotations in parallel for 25K objects in images, see e.g.\ Figure \ref{fig:duck}.
The large number of name annotations per object in \mn gives us a way to reliably derive entry-level names, defined as in Section~\ref{sec:intro} as the most frequent name for an object instance.\footnote{
	The vocabulary of all entry-level names in \mn contains 442 types (the vocabulary of all names is 7970), covering more than 50\% of the objects in \vg, i.e. almost 2M objects in \vg are mentioned in region descriptions with one of these 442 entry-level names.
}
Moreover, the fact that these objects are diverse and visually situated in real-world scenes aligns with our view (see Section~\ref{sec:intro}) that entry-level name should be characterized at an instance-level, not at the class-level (cf.\ Section~\ref{sec:manynames}.
However, our manual inspection of the \mn data revealed a range of annotation problems, e.g., annotators occasionally named an object different from the one highlighted by the bounding box, or the right object but with an incorrect name.
Although these errors are interesting human data, many of them would not occur in actual language use but are artifacts of the crowdsourcing methodology that uses simple graphical boxes to point workers to the annotation target.
%used for \mn, where there is a financial incentive to complete the task as quickly as possible.
As such they pose challenges for our research goal, which is to see whether the object-naming ability of computational models resembles that of actual language users.
To overcome these we collected a new layer of verification annotations on top of \mn, as follows.

>>>>

%\paragraph{(Entry-Level) Object Naming}
%cognitive science/psychology:\\
%- levels of specificity\\
%- basic-level vs. entry-level\\ 
%- object naming studies
%
%Language + Vision:\\
%Ordonez et al., Zarriess \& Schlangen, ... \\
%- Our work: empirical notion of entry-level
%\cs{Necessary to say something about class vs. category? Otherwise I would just always use class to make things easier.}
%% SHORTENING %%Our work on natural object naming connects research in psycholinguistics, \langvis and computer vision. 
In psycholinguistics, studies of picture naming have found that humans identify objects at a preferred level of abstraction, the so-called basic-level \cite{rosch1976basic,jolicoeur1984pictures}. 
The typicality of the object with respect to this basic-level \category is important for determining the preferred name, i.e.\ the entry-level name: highly typical objects (e.g.,\ a robin) are simply named by their basic-level \category (\name{bird}), while atypical objects (e.g.,\ \name{penguin}) are preferably named by the more specific category.
%% This strictly taxonomic view suggests that entry-level names generally hold for all instances of a \category (e.g.,\ penguin).   \mw{Not true!!}
\newcite{Ordonez:2016} take up this view and train a model to map an object's \category detected by an object recognition system to its natural name, guided by external resources like corpus statistics.
By contrast, we rely on the \mn dataset (more details below) to directly test as well as fine-tune object recognition (and image classification) systems, and without presupposing a taxonomical relationship between the possible names for an object.

@@

%% SHORTENING %% \cs{Need to check Jolicoeur and their experiments; say sth about shared visual features}
% prototypical visual features common to all its instances (e.g.,\ apples are round, pears are ... (CHECK)).

In Computer Vision a major focus is visual object recognition, with object classification being a core task. 
Neural object classification systems are trained to label the most salient object in an image and often use the ImageNet \cite{imagenet_cvpr09} benchmark that labels images/objects with 1000 fine-grained classes \cite{googlenet,he2016deep}). 
These neural object classifiers have proven extremely useful %% SHORTENING %%in a large range of transfer learning scenarios. They are commonly used 
as pretrained feature extractors in object detection systems that localize objects and predict their labels \cite{fasterrcnn2015}.
For instance, a commonly used object detector in \lv is \citep{anderson2018updown}'s so-called bottom-up model, which is based on a pretrained ResNet classification and finetuned Faster-RCNN \cite{fasterrcnn2015} for object detection and classification on \vg. 
We will use pretrained ResNet, Faster-RCNN and Bottom-up as models in this paper, extending and testing them for entry-level object naming.

\paragraph{The ManyNames dataset}
The \mn dataset (Anonymous, under review) which builds upon object annotations in \vg, providing up to 36 name annotations in parallel for 25K objects in images, see e.g.\ Figure \ref{fig:duck}.
The large number of name annotations per object in \mn gives us a way to reliably derive entry-level names, defined as the most frequent name for an object instance.
Its vocabulary of all names has 7970 types; restricted to entry-level names it has 442 types (still covering over 50\% of the objects in \vg).
	%% SHORTENING %%The vocabulary of all entry-level names in \mn contains 442 types (the vocabulary of all names is 7970), covering more than 50\% of the objects in \vg, i.e. almost 2M objects in \vg are mentioned in region descriptions with one of these 442 entry-level names.
The fact that these objects are diverse and visually situated in real-world scenes aligns with our view that entry-level name should be characterized at an instance-level, not at the class-level.
However, our manual inspection of the \mn data revealed a range of annotation problems, e.g., annotators occasionally named an object different from the one highlighted by the bounding box, or the right object but with an incorrect name.
Although these errors are interesting human data, many of them would not occur in actual language use but are artifacts of the crowdsourcing methodology that uses simple graphical boxes to point workers to the annotation target.
%used for \mn, where there is a financial incentive to complete the task as quickly as possible.
As such they pose challenges for our research goal, which is to see whether the object-naming ability of computational models resembles that of actual language users.
To overcome these we collected a new layer of verification annotations on top of \mn, as follows.
